Going from coarse landings data to fine scale species distribution

### 2022-03-30 Version_M2_plusieurszones/draft/paper_3/paper_3.Rmd
paper_2

We base our approach on the model developped by @alglave_combining_2022. In this framework, all observations were supposed to be realised at the same scale. Here, we extend the framework to potentially provide fine scale predictions from data that have a coarse resolution (landings data) and potentially combine these data with other (more accurate) datasets such as scientific data.

@@

![(\#fig:SchemeRealloc) Schematic representation of the reallocation process.](images/realloc.png)

@@

Then, we extend the simulation-estimation study to several rectangles to get closer to a real case study configuration. We add a spatial random effect in the latent field (for both simulation and estimation) and we also simulate scientific data (in addition to commercial data) to explore the contribution of both datasets in inference. These simulations will be referred as multiple-square simulations.

>>>>

We base our approach on the model developped by @alglave_combining_2022. In this framework, all observations were supposed to be realised at a fine scale. Here, we extend the framework to potentially provide fine scale predictions from data that have a coarse resolution (landings data) and combine these data with other fine scale datasets such as scientific data.

@@

![(\#fig:SchemeRealloc) Schematic representation of the reallocation process. The biomass field (the background field) depends on a covariate and a spatial random effect. The covariate is the $x$ axis. It has a positive effect on biomass values (i.e. biomass is higher on the right of the grid than on the left). The spatial random effect conduct to a hotspot on the bottom-right of the latent field. The study domain is considered as a statistical rectangle (grey square). Fishermen sample catches in areas of poor biomass where the covariate is relatively low (blue points) and in areas of higher biomass where the covariate is higher and eventually in the hotspot of biomass (orange and red points). These catches belong to the same declaration $j$ and are summed to constitute the declaration $D_j=50$. The declaration is declared at the level of the statistical rectangle. From VMS data, we know the fishing positions $x_i$. In standard processing, $D_j$ are then uniformly reallocated over the fishing positions $x_i$. This strongly homogeneizes the catch. In particular, the effect of the habitat is no more evidenced in the reallocated catch $Y_i^*$.](images/realloc.png)

@@

Then, we extend the simulation-estimation study to several rectangles to get closer to a real case study configuration. We add a spatial random effect in the latent field (for both simulation and estimation) and we also simulate scientific data (in addition to commercial data) to explore the contribution of both datasets in inference. These simulations will be referred as "multiple-square simulations".
